NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2017-01-03 ms_nihao_budget.tex
version suggested by the referee

{\bf As a part of the IGM, the circum galactic medium (CGM) is always 
treated as }an major potential
reservoir of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to detect
cold gas in the CGM.  Meanwhile, theoretical work has predicted that a
substantial  portion of the CGM is in the warm or hot phase with
temperature T $> 10^{4.5}$ K.  Gas enters this phase through
photoionization, accretion shocks or shocks caused by galactic winds
\citep{Voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, so
the detection is dominated by metal lines, e.g. \ovi{}.  Recent
advances in the detection of gas in the CGM have come  from the COS
survey \citep{Tumlinson11, Tumlinson13, Thom12,  Werk12, Werk13}.  On
the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
significant amount of warm ($10^4 < T <5\times 10^6$K) gas has been detected
\citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
future such observations will be extended to a wider range of halo
masses.  A number of large volume cosmological simulations
\citep{Ford13, Ford16, Suresh15, Oppenheimer16} and zoom-in
cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
given  predictions for the \hi{} and \ovi{} absorption
lines. \citet{Gutcke16} compared the column density profile of \ovi{}
and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
cosmological hydrodynamical simulation suite with observations,
studied the covering fraction of dense \hi{}, looked at the shape of
the CGM and its chemical composition. The simulations
  reproduce  the observational covering fraction and column density
  profile of cool \hi{} well, and recover the observed trends of
  \ovi{} column density with luminosity and impact parameter. In
  common with other simulations, however, the column density of \ovi{}
  is lower and the extent of optically thick \hi{} is smaller than
  observed.

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
\citet{Muratov15} showed similar results that the gas and
baryon fractions are lower at lower redshift, after powerful
outflows at intermediate redshift $z \approx 0.5-2$ remove a large
amount of gas from the halo. {\bf Several simulations 
\citep[e.g.,][]{Crain10, Christensen16,Voort16}} found the baryon fraction
and gas fraction are reduced compared to the cosmic baryon
fraction, especially in low mass haloes.
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

@@

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project
\citep{Wang15}.   The initial conditions are created to keep the same
numerical resolution across the whole mass range with typically a
million dark matter particles inside the virial radius of the target
halo at  redshift $z=0$.  The halos to be re-simulated at higher
resolution with baryons have been extracted from 3 different pure
N-body simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.   {\bf Dark
  matter particle masses range from $\sim 10^{4} \Msun$ in  our lowest
  mass haloes to $\sim 10^{6} \Msun$ in our most massive  haloes, and
  their force softenings range from $\sim$ 150 pc to $\sim$ 900 pc,
  respectively Gas particles are less massive by factor of
  $(\Omega_{\rm dm}/\Omega_{\rm b})\simeq 5.48$, and  the
  corresponding force softenings are 2.34 times smaller.}  More
information on the collisionless parent simulations, the force
softenings and particle masses for the highest refinement level for
each simulation and sample  selection can be found in \citet{Dutton14}
and \citet{Wang15}.

@@

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius  to the fiducial baryonic mass for
the most massive galaxy in each zoom-in region. We present the
fractions of total stellar mass {\bf within 20\% $R_{200}$} (blue
points),  and the total baryonic mass including stellar mass plus gas
mass (green points).  For the stellar mass fraction we also show the
relations from halo abundance  matching \citep{Moster13, Behroozi13,
  Kravtsov14}.  The grey area is the one sigma scatter around the mean
value  from \citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all
haloes in our study contain less than the universal fraction of
baryons. The upper panel uses a linear y-axis scale, which highlights
the large amount of baryons that are missing, especially in low mass
haloes. The logarithmic scale in the lower panel highlights the
power-law nature of the relations.

@@

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=budget_res.eps,width=0.95\textwidth}
}
\caption{{\bf Baryon content of NIHAO simulations as a function of
    halo mass color coded by number of dark matter particles per
    halo. This shows the stars and gas content of the simulations is
    insensitive to order of magnitude changes in particle
    resolution.}}
\label{fig:budget_res}
\end{figure*}

Since most of the haloes we study are above the mass where the cosmic
UV background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons.  This
is consistent with expectations from energy driven gas outflows, where
the lower star formation efficiency is more than compensated by the
shallower potential wells of lower mass halos according {\bf to} the
mass loading factor and circular velocity  {\bf relation }$\eta
\propto V^{-2}$ \citep[e.g.,][]{Dutton12, Christensen16}.

@@

As might be expected, haloes with the highest masses  we study ($\sim
10^{12}\Msun$) have high baryon fractions ($\sim 0.7$) with relatively
small scatter (0.05 dex). As halo mass decreases, the baryon fraction
decreases and the scatter increases reaching a maximum of $\sim 0.24$
dex in haloes of mass $\sim 4\times10^{10}\Msun$.  However, at the
lowest halo masses we study, below $10^{10}\Msun$, the scatter starts
to decrease. By contrast the scatter in the stellar mass fraction
increases below this scale. Thus it seems unlikely that stellar
feedback is primarily responsible for the low baryon
fractions. Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. The
baryon fractions {\bf in low mass haloes} are thus controlled primarily 
by the halo masses, and thus are independent of the large scatter in the
{\bf stellar mass}.

%% FIGURE 3
\begin{figure*}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
}
\caption{Comparison between baryon (upper panels) and stellar
    fractions (lower panels) in the NIHAO simulations (blue circles)
    with simulations from \citet{Voort16} (left, red pentagons) and
    \citet{Christensen16} (right, purple pentagons).}
\label{fig:fire_com}
\end{figure*}

@@

In summary, while the stellar mass fractions are dependent on the
sub-grid models, the baryon fractions (for haloes in the mass range
$10^{10}\lta M_{200} \lta 10^{12}\Msun$) appear insensitive to the
details of the simulation code. In particular all three codes predict a
greater fraction of missing baryons in lower mass haloes. This
suggests that the potential well of the halo {\bf correlates the baryon
fraction more closely} than the strength of the feedback.

@@

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass includes
gas and stars that belong to nearby lower mass haloes.  {\bf It is a
  radius within the high-resolution volume of the simulations since
  the contamination fraction in a shell between 0.9 and  1.0 $\Rbar$
  shows most NIHAO galaxies have a fraction close to 0, with largest
  only around 10 - 20\%. } Fig.~\ref{fig:missvr} shows the baryon
radius of each galaxy as function of the virial mass. In physical
units, we find that the baryon radius generally increases with virial
mass. When normalized by the virial radius, the distance baryons are
ejected gradually decreases as halo mass increases, varying from
$\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$ to
$\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.

@@

In Fig.~\ref{fig:inout}, we show the mass fractions of gas (in three
phases) inside the virial radius (filled blue points) and between the
virial and baryon radius (open red points).  {\bf All fractions are
  relative to the fiducial baryonic mass within the  virial radius}.
%
The fractions of cold gas, $f_{\rm cold}$, are shown in the left
panel.  Inside the virial radius $f_{\rm cold}$ increases gradually
from zero at a halo mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo
mass of $10^{12}\Msun$.  The gas outside the virial radius has the
opposite and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of
mass $10^{10}\Msun$ and decreases to zero by halo masses of
$10^{11}\Msun$.
%
The fractions of cool gas, $f_{\rm cool}$, are shown in the middle
panel.  Inside the virial radius, $f_{\rm cool}$, has a maximum of
40\% at a halo mass of $10^{11} \Msun$, and declines to less than 10\%
below and above halo masses of $10^{10}\Msun$ and $10^{12}\Msun$,
respectively.  For most haloes there is more cool gas outside than
inside the virial radius.  In haloes of mass $10^{10}\Msun$, $f_{\rm
  cool}\sim 80\%$, and decreases to less than 10\% by a halo mass of
$10^{12}\Msun$.
%
The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
right panel.  The trends of the gas inside and outside the virial
radius are quite similar, $f_{\rm warm}$ increases monotonically with
halo mass with maximum values of $\sim 30\%$.
%
The hot gas isn't shown since it is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo masses in the range
$10^{10} \lta M_{200}\lta 10^{11} \Msun$, the majority of baryons
associated with the dark matter halo are in the cold and cool phases,
and are located well outside of virial radius.  For haloes in the mass
range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
gas, cool gas and  warm-hot gas are comparable.

@@

The COS-HALOs survey is filling in details about the CGM at low
redshift \citep{Peeples14, Tumlinson11, Tumlinson13, Werk12, Werk13,
  Werk14}.  For the CGM of low-redshift $\sim L^*$ galaxies
($\Mstar\sim 10^{10.5}\Msun$), \citet{Tumlinson13} and
\citet{Peeples14} constrain the mass of  the warm-hot CGM ($T \sim
10^{5-6.7}$K), \citet{Werk14} provides a strict lower limit to the
mass of cool material ($T \sim 10^{4-5}$K) in the CGM of these
galaxies.  In a study using X-rays, \citet{Anderson13} place a
constraints on the mass of  hot gas ($T > 5\times10^6$K) residing in
the extended hot halos.  These observational constraints are shown in
Fig.~\ref{fig:comparison} with the same colour scheme as in Fig.11 of
\citet{Werk14}.  The stellar mass fractions are based on halo
abundance matching as described in \citet{Kravtsov14}, while the cold
disk gas mass comes from \citet{Dutton11}.  {\bf The upper limits to
  the missing fraction are calculated using the lower limits to all
  the fractions. There are two upper limits shown which correspond to
  the two measurements of the cool-gas fraction
  \citep{Werk14,Stern16}. The lower limit to the missing fraction is
  consistent with zero.}

@@

{\bf Since \citet{Crain10} and \citet{Voort13} show that  soft X-ray
  emission traces gas with temperatures a few times the  virial
  temperature (T$_{\rm vir} = 10^6$ K for M$_{200} \sim  10^{12}
  \Msun$), we also estimate the hot gas fraction with lower boundaries
  ($3\times 10^6$ K and $10^6$ K) between the hot gas and  warm-hot
  gas. The hot gas fractions increase to 0.00511 ($3\times 10^6$K)
  and 0.0417 ($10^6$ K), while the warm-hot gas fractions decrease by
  a corresponding amount. Even with these different definitions the
  NIHAO simulations are in good agreement with the observed warm-hot
  and hot gas fractions. }

@@

  A recent estimation for the baryonic fractions from a set of eight
  Milky Way-sized zoom-in cosmological simulations \citep{Colin16} is
  generally {\bf consistent} with our results. The fraction of cool gas
  from their simulations is even lower  ($f_{\rm cool}$ = 0.034) than
  ours and the result from  \citet{Stern16}. On the other hand,
  \citet{Peeples14} gave  a conservative observational estimate about
  warm-hot gas and showed that the fraction of gas in this phase is
  only 5\%,  which is the lower limit of the estimates from
  \citet{Werk14}  and less than the average values from
  \citet{Colin16}  ($f_{\rm warm-hot} \approx 24\%$) and our finding
  ($f_{\rm warm-hot} \approx 17\%$). Therefore, the mix of
  temperatures of the CGM has large uncertainties. More accurate
knowledge of the physical properties of the CGM are necessary to
better constrain feedback models and to understand the role of the CGM
in galaxy formation.

@@

\item Cold gas ($T<10^4$K) is mostly restricted to be within 0.2
  virial radii (Fig.~\ref{fig:corona}). Cool gas ($10^4 < T < 10^5$K)
  dominates the baryonic mass outside the virial radius, {\bf as well
    as outside 20\% $R_{200}$}, at low masses ($M_{200}\lta 3\times
  10^{11} \Msun$) while the warm-hot gas ($10^5 < T <5\times 10^6$K)
  dominates at high masses ($M_{200}\gta 3\times 10^{11} \Msun$)
  (Figs.~\ref{fig:corona} \& \ref{fig:inout}).

@@

%X-ray coronae in simulations of disc galaxy formation
\bibitem[Crain et al.(2010)]{Crain10}
Crain, R.~A., McCarthy, I.~G., Frenk, C.~S., et al.\ 2010, \mnras, 470, 1403

@@

>>>>

As a part of the IGM, the circum galactic medium (CGM) is always 
treated as an major potential
reservoir of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to detect
cold gas in the CGM.  Meanwhile, theoretical work has predicted that a
substantial  portion of the CGM is in the warm or hot phase with
temperature T $> 10^{4.5}$ K.  Gas enters this phase through
photoionization, accretion shocks or shocks caused by galactic winds
\citep{Voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, so
the detection is dominated by metal lines, e.g. \ovi{}.  Recent
advances in the detection of gas in the CGM have come  from the COS
survey \citep{Tumlinson11, Tumlinson13, Thom12,  Werk12, Werk13}.  On
the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
significant amount of warm ($10^4 < T <5\times 10^6$K) gas has been detected
\citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
future such observations will be extended to a wider range of halo
masses.  A number of large volume cosmological simulations
\citep{Ford13, Ford16, Suresh15, Oppenheimer16} and zoom-in
cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
given  predictions for the \hi{} and \ovi{} absorption
lines. \citet{Gutcke16} compared the column density profile of \ovi{}
and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
cosmological hydrodynamical simulation suite with observations,
studied the covering fraction of dense \hi{}, looked at the shape of
the CGM and its chemical composition. The simulations
  reproduce  the observational covering fraction and column density
  profile of cool \hi{} well, and recover the observed trends of
  \ovi{} column density with luminosity and impact parameter. In
  common with other simulations, however, the column density of \ovi{}
  is lower and the extent of optically thick \hi{} is smaller than
  observed.

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
\citet{Muratov15} showed similar results that the gas and
baryon fractions are lower at lower redshift, after powerful
outflows at intermediate redshift $z \approx 0.5-2$ remove a large
amount of gas from the halo. Several simulations 
\citep[e.g.,][]{Crain07, Christensen16,Voort16} found the baryon fraction
and gas fraction are reduced compared to the cosmic baryon
fraction, especially in low mass haloes.
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

@@

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project
\citep{Wang15}.   The initial conditions are created to keep the same
numerical resolution across the whole mass range with typically a
million dark matter particles inside the virial radius of the target
halo at  redshift $z=0$.  The halos to be re-simulated at higher
resolution with baryons have been extracted from 3 different pure
N-body simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.   Dark
  matter particle masses range from $\sim 10^{4} \Msun$ in  our lowest
  mass haloes to $\sim 10^{6} \Msun$ in our most massive  haloes, and
  their force softenings range from $\sim$ 150 pc to $\sim$ 900 pc,
  respectively Gas particles are less massive by factor of
  $(\Omega_{\rm dm}/\Omega_{\rm b})\simeq 5.48$, and  the
  corresponding force softenings are 2.34 times smaller.  More
information on the collisionless parent simulations, the force
softenings and particle masses for the highest refinement level for
each simulation and sample  selection can be found in \citet{Dutton14}
and \citet{Wang15}.

@@

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius  to the fiducial baryonic mass for
the most massive galaxy in each zoom-in region. We present the
fractions of total stellar mass within 20\% $R_{200}$ (blue
points),  and the total baryonic mass including stellar mass plus gas
mass (green points).  For the stellar mass fraction we also show the
relations from halo abundance  matching \citep{Moster13, Behroozi13,
  Kravtsov14}.  The grey area is the one sigma scatter around the mean
value  from \citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all
haloes in our study contain less than the universal fraction of
baryons. The upper panel uses a linear y-axis scale, which highlights
the large amount of baryons that are missing, especially in low mass
haloes. The logarithmic scale in the lower panel highlights the
power-law nature of the relations.

@@

Since most of the haloes we study are above the mass where the cosmic
UV background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons.  This
is consistent with expectations from energy driven gas outflows, where
the lower star formation efficiency is more than compensated by the
shallower potential wells of lower mass halos according to the
mass loading factor and circular velocity  relation $\eta
\propto V^{-2}$ \citep[e.g.,][]{Dutton12, Christensen16}.

@@

As might be expected, haloes with the highest masses  we study ($\sim
10^{12}\Msun$) have high baryon fractions ($\sim 0.7$) with relatively
small scatter (0.05 dex). As halo mass decreases, the baryon fraction
decreases and the scatter increases reaching a maximum of $\sim 0.24$
dex in haloes of mass $\sim 4\times10^{10}\Msun$.  However, at the
lowest halo masses we study, below $10^{10}\Msun$, the scatter starts
to decrease. By contrast the scatter in the stellar mass fraction
increases below this scale. Thus it seems unlikely that stellar
feedback is primarily responsible for the low baryon
fractions. Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. The
baryon fractions in low mass haloes are thus controlled primarily 
by the halo masses, and thus are independent of the large scatter in the
stellar mass.

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
}
\caption{Comparison between baryon (upper panels) and stellar
    fractions (lower panels) in the NIHAO simulations (blue circles)
    with simulations from \citet{Voort16} (left, red pentagons) and
    \citet{Christensen16} (right, purple pentagons).}
\label{fig:fire_com}
\end{figure*}

@@

In summary, while the stellar mass fractions are dependent on the
sub-grid models, the baryon fractions (for haloes in the mass range
$10^{10}\lta M_{200} \lta 10^{12}\Msun$) appear insensitive to the
details of the simulation code. In particular all three codes predict a
greater fraction of missing baryons in lower mass haloes. 
{\bf It suggests that the baryon fraction correlates 
strongly with halo mass, due to the deeper potential well of the halo and/or stronger 
ram pressure experienced by the outflowing gas. However, Fig.~\ref{fig:fire_com}
 suggests that the 
 specific implementation of the feedback model does not matter, as long as the feedback 
is efficient in driving outflows.}

@@

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals the {\bf fiducial
baryonic mass defined by Eq.~\ref{equ:mb}}. This is a lower limit to
the true extent of the missing baryons since the baryon mass includes
gas and stars that belong to nearby lower mass haloes.  It is a
  radius within the high-resolution volume of the simulations since
  the {\bf mass fraction of low resolution dark matter particles}
  in a shell between 0.9 and  1.0 $\Rbar$
  shows most NIHAO galaxies have a fraction close to 0, with largest
  only around 10 - 20\%.  Fig.~\ref{fig:missvr} shows the baryon
radius of each galaxy as function of the virial mass. In physical
units, we find that the baryon radius generally increases with virial
mass. When normalized by the virial radius, the distance baryons are
ejected gradually decreases as halo mass increases, varying from
$\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$ to
$\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.

@@

In Fig.~\ref{fig:inout}, we show the mass fractions of gas (in three
phases) inside the virial radius (filled blue points) and between the
virial and baryon radius (open red points).  All fractions are
  relative to the fiducial baryonic mass within the  virial radius.
%
The fractions of cold gas, $f_{\rm cold}$, are shown in the left
panel.  Inside the virial radius $f_{\rm cold}$ increases gradually
from zero at a halo mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo
mass of $10^{12}\Msun$.  The gas outside the virial radius has the
opposite and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of
mass $10^{10}\Msun$ and decreases to zero by halo masses of
$10^{11}\Msun$.
%
The fractions of cool gas, $f_{\rm cool}$, are shown in the middle
panel.  Inside the virial radius, $f_{\rm cool}$, has a maximum of
40\% at a halo mass of $10^{11} \Msun$, and declines to less than 10\%
below and above halo masses of $10^{10}\Msun$ and $10^{12}\Msun$,
respectively.  For most haloes there is more cool gas outside than
inside the virial radius.  In haloes of mass $10^{10}\Msun$, $f_{\rm
  cool}\sim 80\%$, and decreases to less than 10\% by a halo mass of
$10^{12}\Msun$.
%
The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
right panel.  The trends of the gas inside and outside the virial
radius are quite similar, $f_{\rm warm}$ increases monotonically with
halo mass with maximum values of $\sim 30\%$.
%
The hot gas isn't shown since it is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo masses in the range
$10^{10} \lta M_{200}\lta 10^{11} \Msun$, the majority of baryons
associated with the dark matter halo are in the cold and cool phases,
and are located well outside of virial radius.  For haloes in the mass
range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
gas, cool gas and  warm-hot gas are comparable.

@@

The COS-HALOs survey is filling in details about the CGM at low
redshift \citep{Peeples14, Tumlinson11, Tumlinson13, Werk12, Werk13,
  Werk14}.  For the CGM of low-redshift $\sim L^*$ galaxies
($\Mstar\sim 10^{10.5}\Msun$), \citet{Tumlinson13} and
\citet{Peeples14} constrain the mass of  the warm-hot CGM ($T \sim
10^{5-6.7}$K), \citet{Werk14} provides a strict lower limit to the
mass of cool material ($T \sim 10^{4-5}$K) in the CGM of these
galaxies.  In a study using X-rays, \citet{Anderson13} place a
constraints on the mass of  hot gas ($T > 5\times10^6$K) residing in
the extended hot halos.  These observational constraints are shown in
Fig.~\ref{fig:comparison} with the same colour scheme as in Fig.11 of
\citet{Werk14}.  The stellar mass fractions are based on halo
abundance matching as described in \citet{Kravtsov14}, while the cold
disk gas mass comes from \citet{Dutton11}.  The upper limits to
  the missing fraction are calculated using the lower limits to all
  the fractions. There are two upper limits shown which correspond to
  the two measurements of the cool-gas fraction
  \citep{Werk14,Stern16}. The lower limit to the missing fraction is
  consistent with zero.

@@

 Since \citet{Crain07} and \citet{Voort13} show that  soft X-ray
  emission traces gas with temperatures a few times the  virial
  temperature (T$_{\rm vir} = 10^6$ K for M$_{200} \sim  10^{12}
  \Msun$), we also estimate the hot gas fraction with lower boundaries
  ($3\times 10^6$ K and $10^6$ K) between the hot gas and  warm-hot
  gas. The hot gas fractions increase to 0.00511 ($3\times 10^6$K)
  and 0.0417 ($10^6$ K), while the warm-hot gas fractions decrease by
  a corresponding amount. Even with these different definitions the
  NIHAO simulations are in good agreement with the observed warm-hot
  and hot gas fractions.

@@

  A recent estimation for the baryonic fractions from a set of eight
  Milky Way-sized zoom-in cosmological simulations \citep{Colin16} is
  generally consistent with our results. The fraction of cool gas
  from their simulations is even lower  ($f_{\rm cool}$ = 0.034) than
  ours and the result from  \citet{Stern16}. On the other hand,
  \citet{Peeples14} gave  a conservative observational estimate about
  warm-hot gas and showed that the fraction of gas in this phase is
  only 5\%,  which is the lower limit of the estimates from
  \citet{Werk14}  and less than the average values from
  \citet{Colin16}  ($f_{\rm warm-hot} \approx 24\%$) and our finding
  ($f_{\rm warm-hot} \approx 17\%$). Therefore, the mix of
  temperatures of the CGM has large uncertainties. More accurate
knowledge of the physical properties of the CGM are necessary to
better constrain feedback models and to understand the role of the CGM
in galaxy formation.

@@

\item Cold gas ($T<10^4$K) is mostly restricted to be within 0.2
  virial radii (Fig.~\ref{fig:corona}). Cool gas ($10^4 < T < 10^5$K)
  dominates the baryonic mass outside the virial radius, as well
    as outside 20\% $R_{200}$, at low masses ($M_{200}\lta 3\times
  10^{11} \Msun$) while the warm-hot gas ($10^5 < T <5\times 10^6$K)
  dominates at high masses ($M_{200}\gta 3\times 10^{11} \Msun$)
  (Figs.~\ref{fig:corona} \& \ref{fig:inout}).

@@

%The baryon fraction of CDM haloes
\bibitem[Crain et al.(2007)]{Crain07}
Crain, R.~A., Eke, C.~R., Frenk, C.~S., et al.\ 2007, \mnras, 377, 41

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Resolution test}

%% FIGURE in APPENDICES
\begin{figure*}
\centerline{
  \psfig{figure=budget_res.eps,width=0.95\textwidth}
}
\caption{Baryon content of NIHAO simulations as a function of
    halo mass color coded by number of dark matter particles per
    halo. This shows the stars and gas content of the simulations is
    insensitive to order of magnitude changes in particle
    resolution.}
\label{fig:budget_res}
\end{figure*}
